Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-20 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Updated precip validation. No legend and bigger figures

```{r}
my_hurricanes <- c("Floyd-1999", 
                   "Irene-2011", 
                   "Lee-2011", 
                   "Ike-2008",
                   "Allison-2001")
pdf("validate_precip.pdf", height = 8, width = 12)
for(hurricane in my_hurricanes){
        a <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -3) + theme(legend.position="none")
        a <- map_tracks(storm = hurricane, 
                        plot_object = a, plot_points = FALSE)
        b <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -2) + theme(legend.position = "none")
        b <- map_tracks(storm = hurricane, 
                        plot_object = b, plot_points = FALSE)
        c <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -1) + theme(legend.position = "none")
        c <- map_tracks(storm = hurricane, 
                        plot_object = c, plot_points - FALSE)
        d <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 0) + theme(legend.position = FALSE)
        d <- map_tracks(storm = hurricane, 
                        plot_object = d, plot_points = FALSE)
        e <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 1) + theme(legend.position = "none")
        e <- map_tracks(storm = hurricane, 
                        plot_object = e, plot_points = FALSE)
        f <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 2) + theme(legend.position = "none")
        f <- map_tracks(storm = hurricane, 
                        plot_object = f, plot_points = FALSE)
        g <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 3) + theme(legend.position = "none")
        g <- map_tracks(storm = hurricane, 
                        plot_object = g, plot_points = FALSE)
        precip_plot <- grid.arrange(a, b, c, d, e, f, g, nrow = 2,
                                    top = textGrob(paste0("7-Day Precipitation For\n Storm ", hurricane)))
        print(precip_plot)
}
dev.off()
```

>>>>

```{r}
my_hurricanes <- c("Floyd-1999", 
                   "Irene-2011", 
                   "Lee-2011", 
                   "Ike-2008",
                   "Allison-2001")
pdf("validate_precip.pdf", height = 8, width = 12)
for(hurricane in my_hurricanes){
        a <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -3) + theme(legend.position="none")
        a <- map_tracks(storm = hurricane, 
                        plot_object = a, plot_points = FALSE)
        b <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -2) + theme(legend.position = "none")
        b <- map_tracks(storm = hurricane, 
                        plot_object = b, plot_points = FALSE)
        c <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = -1) + theme(legend.position = "none")
        c <- map_tracks(storm = hurricane, 
                        plot_object = c, plot_points = FALSE)
        d <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 0) + theme(legend.position = "none")
        d <- map_tracks(storm = hurricane, 
                        plot_object = d, plot_points = FALSE)
        e <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 1) + theme(legend.position = "none")
        e <- map_tracks(storm = hurricane, 
                        plot_object = e, plot_points = FALSE)
        f <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 2) + theme(legend.position = "none")
        f <- map_tracks(storm = hurricane, 
                        plot_object = f, plot_points = FALSE)
        g <- map_counties(storm = hurricane, metric = "rainfall",
                          days_included = 3) + theme(legend.position = "none")
        g <- map_tracks(storm = hurricane, 
                        plot_object = g, plot_points = FALSE)
        precip_plot <- grid.arrange(a, b, c, d, e, f, g, nrow = 2,
                                    top = textGrob(paste0("7-Day Precipitation For\n Storm ", hurricane)))
        print(precip_plot)
}
dev.off()
```
